### 2014-04-05 LaTeX/PreezeText.tex
MPSA presentation update

\begin{itemize}
	\item Civil War $\rightarrow$ Economic Performance
	\item Economic Performance $\rightarrow$ Civil War
	\item Disaggregating Civil Wars
\end{itemize}

>>>>

\begin{itemize}
	\item Civil War $\rightarrow$ Economic Performance
	\begin{itemize}
	\item Collier (1999) - \emph{destruction, disruption, diversion, dissaving, portfolio substitution}
	\item Kang \& Meernik (2005) - seek to explain rapid or stagnant post-war recovery
	\end{itemize}
	\item Economic Performance $\rightarrow$ Civil War
	\begin{itemize}
	\item Collier et al. (2003) - the conflict trap
	\item Miguel et al (2004) - rainfall IV for economic shocks
	\end{itemize}
	\item Disaggregating Civil Wars
	\begin{itemize}
	\item Pierskalla \& Hollenbach (2013) - cell phone coverage $\rightarrow$ rebel mobilization
	\end{itemize}
\end{itemize}
